---
title: "Regression models Project"
output: html_document
---

#Executive Summary
In my study of mtcars dataset, I found that manual transmission can improve on the mileage (mpg) of the vehicle.

I approached the problem by first looking the data by exploratory analysis. Then I fit linear models using the best subset method provided by the *leaps* package. Three models with largeest adjust $R^2$ were comprared using ANOVA.Finally, I also drew some residual plots to confirm that my linear model was indeed correct.


```{r}
data(mtcars)
mtcars$am <- factor(mtcars$am,labels=c("Automatic","Manual"))
with(mtcars,plot(am,mpg,xlab="Transmission",ylab="Miles/(US) gallon",main="Miles/(US) gallon by Transmission"))
groupmpg <- tapply(mtcars$mpg,mtcars$am,mean)
```

form the plot we can see that manual is better than automatic transmisson regrading mpg(Miles/(US) gallon), which can improve `r round(groupmpg[2]-groupmpg[1],digits=2)` Miles/(US) gallon.

We have control other counders to reveal the real effect of *transmisson* of *mpg*. here I use the package `leaps` to evaluate all the best-subset models.
```{r}
library(leaps)
regfit.full=regsubsets(mpg~.,data=mtcars, nvmax=10)
reg.summary=summary(regfit.full)
plot(reg.summary$adjr2,xlab="Number of Variables",ylab="adjr2")

```

from the plot we can see that models with 3-6 variables are have relative higher adjust $R^2$. using the command ` summary(regfit.full)` will show ` wt,qsec,am` are nessary, and `hp,disp,drat ` will be added to the model  cumulativly. and I will usging ANOVA to compare these nest models.the result show there  is no significant difference betwen these models , so I will choose the simplest one.

```{r}
fit1 <- lm(mpg~wt + qsec + am,data=mtcars)
```
*conclusion*: Manual is better than automatic transmisson, which will improve the mileage (mpg) by `r round(coef(fit1)[4],digits=2)` Miles/(US) gallon, with $95\%CI$ `r round(confint(fit1)[4,1],digits=2)` - `r round(confint(fit1)[4,2],digits=2)` Miles/(US) gallon.

confint(fit1)[4,1]

#Appendix
```{r}
par(mfrow=c(2,2))
plot(fit1)
```



